Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper: add implementation section

\section{Experiments}\label{sec:experiments}
To evaluate the performance of our approach,  we implemented
a prototype system in Java, following a traditional iterator model.
For our experiments we plan and execute queries
for three separate survey-based data sets, showing that our system
is well suited for early dataset exploration.

>>>>

\section{Experiments}\label{sec:experiments}
For our experiments we plan and execute queries for three separate survey-based data sets, showing that our system is well suited for early dataset exploration.
We show that \ProjectName{} performs an order of magnitude better than imputation on the full dataset and produces results of comparable quality.

\subsection{Implementation}
To evaluate the performance of our approach, we implemented a prototype system in Java, following a traditional iterator model.
Our database handles a subset of standard SQL queries, including filters, joins, projection, grouping and aggregation.
For simplicity, \ProjectName{} only handles tables containing integer data, so we pre-process our experimental datasets before loading them.
